Approximation as Differentiation

### 2025-07-08 main/related-work.tex
'language' no longer needed in notes.
Tweaks.
Purging section 4.
Bit more blurb on tangent categories.

\section{Related work}
\label{sec:related-work}

@@

\cite{cockett14,cockett18}

>>>>

\section{Related Work}
\label{sec:related-work}

@@

\emph{Tangent categories}, due originally to \citet{rosický84} and developed by \citet{cockett14,cockett18},
provide an abstract categorical framework for reasoning about differentiation, inspired by the structure of
the tangent bundle in differential geometry. In a tangent category, each object $X$ is equipped with a tangent
bundle $T(X)$, and each morphism $f: X \to Y$ has a corresponding differential map $T(f): TX \to TY$
satisfying axioms analogous to the chain rule and linearity of differentiation. Tangent categories generalise
Cartesian differential categories \cite{cdcs}, which model differentiation over Cartesian closed categories
using a syntactic derivative operator. The motivation behind tangent categories is to \roly{Bob to say
something here..}
